infer: An R package for tidyverse-friendly statistical inference

### 2021-06-24 figs/paper/paper.tex
spellcheck

\begin{itemize}
\tightlist
\item
  \texttt{visualize()} plots the null distribution of test statistics

  \begin{itemize}
  \tightlist
  \item
    \texttt{shade\_p\_value()} situates the observed statistic in the
    null distribution, shading the region as or more extreme
  \item
    \texttt{shade\_confidence\_interval()} situates the confidence
    interval region in the null distribution, shading the region with
    the bounds
  \end{itemize}
\item
  \texttt{get\_p\_value()} calculates a p-value via the juxtaposition of
  the test statistic and null distribution
\item
  \texttt{get\_confidence\_interval()} calculates a confidence interval
  via the juxtaposition of the test statistic and null distribution
\end{itemize}

@@

\texttt{broom} and \texttt{parameters} convert model objects to unified
output formats, though do not provide methods for fitting models,
describing null distributions, or calculating summary statistics from
tabular data. \texttt{statsexpressions}, and adjacent packages in the
\texttt{easystats} ecosystem, implement wrappers with consistent
interfaces for theory-based hypothesis tests. The structure of each of
these packages is defined by model types, where each model type has its
own associated function and/or model object. In contrast, \texttt{infer}
is structured around four functions, situating statistics and model
types within a more abstracted grammar. \texttt{infer}'s initial release
on the Comprehensive R Archive Network predated that of each of the
packages mentioned above, with the exception of \texttt{broom} (R Core
Team, 2021).

>>>>

\begin{itemize}
\tightlist
\item
  \texttt{visualize()} plots the null distribution of test statistics.

  \begin{itemize}
  \tightlist
  \item
    \texttt{shade\_p\_value()} situates the observed statistic in the
    null distribution, shading the region as or more extreme.
  \item
    \texttt{shade\_confidence\_interval()} situates the confidence
    interval region in the null distribution, shading the region within
    the bounds.
  \end{itemize}
\item
  \texttt{get\_p\_value()} calculates a p-value via the juxtaposition of
  the test statistic and null distribution.
\item
  \texttt{get\_confidence\_interval()} calculates a confidence interval
  via the juxtaposition of the test statistic and null distribution.
\end{itemize}

@@

\texttt{broom} and \texttt{parameters} convert model objects to unified
output formats, though do not provide methods for fitting models,
describing null distributions, or calculating summary statistics from
tabular data. \texttt{statsexpressions}, and adjacent packages in the
\texttt{easystats} ecosystem, implement wrappers with consistent
interfaces for theory-based hypothesis tests. At a higher level, the
structure of each of these packages is defined by model types, where
each model type has its own associated function and/or model object. In
contrast, \texttt{infer} is structured around four functions, situating
statistics and model types within a more abstracted grammar.
\texttt{infer}'s initial release on the Comprehensive R Archive Network
predated that of each of the packages mentioned above, with the
exception of \texttt{broom} (R Core Team, 2021).
